MR-PFU: A suite of R packages for energy conversion chain analysis

### 2023-07-28 paper.Rmd
Better footnote.

We created a suite of `R` packages 
to assist SEA practitioners to analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the MR-PFU database,^["MR-PFU" 
is an initialism for "Multi-Region
Primary, Final, Useful."
The MR-PFU database is multi-regional in the sense that
it contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames, 
not SQL or similar databases.] 
a new resource for the SEA community [@Marshall:2023aa].

>>>>

We created a suite of `R` packages 
to assist SEA practitioners to analyze 
energy movement through society. 
The new packages enable analysis of any country in the world
across timespans of decades or longer.
In short, the packages enable, for the first time, scalable SEA.
We used the new packages to create the MR-PFU database,^["MR-PFU" 
is an initialism for "Multi-Region
Primary, Final, Useful."
The MR-PFU database is "multi-regional" in the sense that
it contains many countries as well as 
continental and world aggregations.
Technically speaking, 
we create [matsindf][link-matsindf] data frames, 
not SQL or similar databases.] 
a new resource for the SEA community [@Marshall:2023aa].
